---
title: "Analysis of Cats Data"
author: "Akshaya Padhi"
date: "6/3/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shine App

Find the shinyApp at:
https://akpadhi.shinyapps.io/assignment_wk4/

* Cats K-means clusting based on the "cats" data from library MASS.
* To use this application, select x and y variables.  
* Choice boxes include Body Weight (Bwt) and Heart weight (Hwt) as options.  
* Slide the the slider to chose the number of clusturs.



## Anatomical Data from Domestic Cats
###Description
The heart and body weights of samples of male and female cats used for digitalis experiments. The cats were all adult, over 2 kg body weight.

This data frame contains the following columns:

- Sex: Factor with evels "F" and "M"
- Bwt: body weight in kg
- Hwt: heart weight in g

## Slide with R Output

```{r echo = FALSE, message=FALSE, warning=FALSE}
require(dplyr)
require(ggplot2)
require(GGally)
require(MASS)
data(cats)

```

```{r echo = TRUE}
head(cats)
```

## Exploratory Analysis of the Data


```{r echo = FALSE, message=FALSE, warning=FALSE}

ggpairs(cats, lower = list(continuous = wrap("smooth")), ggplot2::aes(colour=Sex))+
    ggtitle("Analysis of Cats Data")+theme_bw() +
    theme(
                             plot.title = element_text(size = rel(1.8), 
                                                       color = "black", face = "bold", hjust = 0.5),
                             plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
                             
```

